Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-10-11 doc/paper.tex
adding acknowledments to paper

@@

% Authors
\author[1]{Manuel Razo-Mejia}
\author[2,3,4]{Madhav Mani}
\author[1,5,*]{Dmitri Petrov}

% Affiliations
\affil[1]{Department of Biology, Stanford University, Stanford, CA, USA}
\affil[2]{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Chicago, IL, USA}
\affil[3]{NSF-Simons Center for Quantitative Biology, Northwestern University, Chicago, IL, USA}
\affil[4]{Department of Molecular Biosciences, Northwestern University, Chicago, IL, USA}
\affil[5]{Stanford Cancer Institute, Stanford University School of Medicine, Stanford, CA, USA}
\affil[*]{Correspondence: dpetrov@stanford.edu}

@@

@@

@@

@@

\printbibliography

>>>>

% Define command to begin the supplementary section
\newcommand{\beginsupplement}{
\setcounter{section}{0} % Restart section counter
\renewcommand{\thesection}{S\arabic{section}}%
\setcounter{table}{0} % Restart table counter
\renewcommand{\thetable}{S\arabic{table}}%
\setcounter{figure}{0} % Restart figure counter
\renewcommand{\thefigure}{S\arabic{figure}}%
\setcounter{equation}{0} % Restart equation counter
\renewcommand{\theequation}{S\arabic{equation}}%
}

@@

% Authors
\author[1]{Manuel Razo-Mejia}
\author[2,3]{Madhav Mani}
\author[1,4,*]{Dmitri Petrov}

% Affiliations
\affil[1]{Department of Biology, Stanford University, Stanford, CA, USA}
\affil[2]{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Chicago, IL, USA}
\affil[3]{NSF-Simons Center for Quantitative Biology, Northwestern University, Chicago, IL, USA}
\affil[4]{Stanford Cancer Institute, Stanford University School of Medicine, Stanford, CA, USA}
\affil[*]{Correspondence: dpetrov@stanford.edu}

@@

% Remove main text from the table of contents by specifying not to include
% any section or subsection
\addtocontents{toc}{\protect\setcounter{tocdepth}{-1}}

% Define reference segment for main text
\begin{refsegment}
% Generate filter to not include references from main text in the
% supplemental references
\defbibfilter{notother}{not segment=\therefsegment}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We would like to thank Griffin Chure and Michael Betancourt for their helpful
advice and discussion. We would like to thank Karna Gowda, Spencer Farrell, and
Shaili Mathur for critical observations on the manuscript. MRM was supported by
the Schmidt Science Fellowship. MM was supported by The National Science
Foundation-Simons Center for Quantitative Biology at Northwestern University and
the Simons Foundation grant 597491. MM is a Simons Investigator.

% Print main text references
\printbibliography[segment=\therefsegment]
% Close reference segment
\end{refsegment}

\clearpage

% SUPPLEMENTAL MATERIAL

% Indicate that now all sections and subsections should be included in the
% table of contents so that only the SI is included.
\addtocontents{toc}{\protect\setcounter{tocdepth}{3}}

% Define reference section for the supplemental material
\begin{refsegment}
% Set equation, table and figure counters to begin with "S"
\beginsupplement

@@

\tableofcontents

@@

% Print supplemental references changing the title
\printbibliography[title={Supplemental References},
segment=\therefsegment, filter=notother]
\end{refsegment}

% \printbibliography
